---
title: "W4 Assignment"
author: "Rizli Anshari"
date: "October 5, 2019"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE, include = FALSE}
set.seed(123)
setwd("C:/Users/avria/Google Drive/!LEARNING/Data Science - 09.Developing Data Products")
library(shiny)
library(leaflet)
library(dplyr)
library(leaflet.extras)

```

## Overview

This is an RStudio shiny application developed as a part of final project in the Developing Data Products course in Coursera Data Science Specialization track. The application summarizes earthquake position which occurs in Indonesia with a magnituted higher than 2.5 richter scale. The earthquake occurs in between September 28th to October 5th, 2019.

## The Application includes the following:

- Form of Input used: Radio Button
- Reactive output displayed as a result of server calculations
- The server.R and ui.R codes are posted on github at: <https://XXX>
- The App can be found at: <https://rizlians.shinyapps.io/w4_assigment/>

## R Code for the Application

```{r, echo = TRUE, warning=FALSE}


#import data
data <- read.csv("earthquake_map.csv")

#categorize earthquake depth
data$depth_type <- ifelse(data$depth <= 70, "shallow", ifelse(data$depth <= 300 | data$depth >70, "intermediate", ifelse(data$depth > 300, "deep", "other")))

#ui function
ui <- fluidPage(
mainPanel( 
leafletOutput(outputId = "mymap"), 
absolutePanel(top = 60, left = 20, 
      checkboxInput("markers", "Depth", FALSE),
      checkboxInput("heat", "Heatmap", FALSE)
    )
))

#server function
server <- function(input, output, session) {
 pal <- colorNumeric(
    palette = c('gold', 'orange', 'dark orange', 'orange red', 'red', 'dark red'),
    domain = data$mag)
  
 pal2 <- colorFactor(
    palette = c('blue', 'yellow', 'red'),
    domain = data$depth_type
  )
  
output$mymap <- renderLeaflet({
    leaflet(data) %>% 
      setView(lng = 134, lat = -6, zoom = 4)  %>% 
      addTiles() %>% 
      addCircles(data = data, lat = ~ latitude, lng = ~ longitude, weight = 1, radius = ~sqrt(mag)*25000, popup = ~as.character(mag), label = ~as.character(paste0("Magnitude: ", sep = " ", mag)), color = ~pal(mag), fillOpacity = 0.5)
})
  
  observe({
    proxy <- leafletProxy("mymap", data = data)
    proxy %>% clearMarkers()
    if (input$markers) {
      proxy %>% addCircleMarkers(stroke = FALSE, color = ~pal2(depth_type), fillOpacity = 0.2,  label = ~as.character(paste0("Magnitude: ", sep = " ", mag))) %>%
        addLegend("bottomright", pal = pal2, values = data$depth_type,
                  title = "Depth Type",
                  opacity = 1)}
    else {
      proxy %>% clearMarkers() %>% clearControls()
    }
  })
  
  observe({
    proxy <- leafletProxy("mymap", data = data)
    proxy %>% clearMarkers()
    if (input$heat) {
      proxy %>%  addHeatmap(lng=~longitude, lat=~latitude, intensity = ~mag, blur =  10, max = 0.05, radius = 15) 
      }
    else{
      proxy %>% clearHeatmap()
      }
  })
}

shinyApp(ui, server)
```


## Earthquake Data in the table
```{r, echo=FALSE, warning=FALSE}
p <- read.csv("earthquake_map.csv")
p
```